%______________________________________________________________________________________________________________________
\documentclass[margin,line]{resume}

\usepackage{color}
\usepackage{xcolor}
\usepackage{tabularx,colortbl}
\usepackage{url}
\definecolor{light-gray}{gray}{.85} 


\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks, urlcolor=linkcolour, linkcolor=linkcolour}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Ahmed Isam Abdelrahim}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    Nationality: Sudanese                            \hfill Date of Birth: 24 - Aug- 1985 \vspace{0mm}\\\vspace{0mm}%
   Marital Status: Single                              \hfill mobile: +966 540894249          \vspace{0mm}\\\vspace{0mm}%
    Website: \url{http://ahmed.sudancs.com}      \hfill e-mail: \href{mailto:suda.nix@hotmail.com}{suda.nix@hotmail.com}  \vspace{0mm}\\\vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Objective
\section{\mysidestyle Objective}
Software engineer with in-depth knowledge looking for challenging position in the field of application development and system programming to gain experience in the field and raise the work efficiency.

    %__________________________________________________________________________________________________________________
    % Summary
    \section{\mysidestyle Summary}
\begin{itemize}
\item +1 year experience in  software development for large scale industry using C,C++ and Qt.
\item Experience in research oriented projects and developing proof of concept and prototype model.
\item Experience in translating on-paper thoughts, through design specification and implementation and verification, into a robust shipping product.
\item Experience in application of cryptographic protocols, Smart card (.NET Gemalto card), Parrallel and GPU programming (OpenCL,CUDA).
\item Experience on software engineering methodologies, practice and tools.
\item Hand-on experience on operating system development, kernel and system programming, free and open source applications/libraries development
\end{itemize}

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Khartoum} - Faculty of Mathematical Sciences. \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelor (BSc) Degree in Computer Sciences} \hfill \textbf{ October 2004 -- July 2010} \\%
    \textsl{Second-class Honours, upper division (2:1)}\vspace{-3mm}\\\vspace{-1mm}%

    %__________________________________________________________________________________________________________________
    % Certification
    \section{\mysidestyle Certification}

    \textbf{Nokia Certified Qt Developer.} \hfill \textbf{November 2010} \vspace{-3mm}\\\vspace{-1mm}%

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Center of Excellence in Information Assurance}, King Saud University , KSA. \vspace{2mm}\\\vspace{1mm}%
    \textsl{\textbf{Software Engineer}} \hfill \textbf{December 2010 -- present}\\
     I am currently serving as software engineer at CoEIA, my main responsibilities include \textsl{gathering and analysis requirments, software desing and implementation, software testing, documentation, assist researchers}. some of projects I was doing in this period :

\begin{itemize}
\item \textbf{Parental Control System (Hajeb) - Software to Control PC and Internet}: 
\begin{itemize}
\item \textsl{Description}: a complete software suite  to constrain the usage of computer and internet. its capable of blocking unwanted web sites and programs , disconnect the Internet with respect to the Allowed Times Table, Monitor keystrokes, Monitor Screen and take Screenshot in a specific times, Sniffing HTTP requests, Manage each user in a separate profile. Also the software has a complete license and update system to generate and validate the serial numbers and doing auto-update for the components.
 
\item  \textsl{Role: Team Lead (Team of one)} : I Architect and design and implement the whole software.

\item  \textsl{Technology/Libraries:} C++, Qt, Win32 API , Layered Service Provider (LSP), SQLite.

\item  \textsl{Project size/Time:} 5 month project,  +7K Line of Code.
\end{itemize}

\item \textbf{Privacy Control (CPC) - Software to Protect PC Privacy :}
\begin{itemize}
\item  \textsl{Description} : Developed a high level security application designed to help you completely eliminate sensitive information from your computer, protect your Internet privacy, and enhance system performance. CPC also functions as a wonderful clean up utility by removing useless files that slow down your computer. 

\item  \textsl{Role: developer (Team of Three)} : I've involved in the desing and architect of the software, implement the most of the GUI stuff and help the developers to write custom model and custom tree to hold the data.

\item  \textsl{Technology/Libraries:} C++, Qt, Win32 API, PHP, MySQL.

\item  \textsl{Project size/Time:} 3 month project,  +5K Line of Code.
\end{itemize}

\item \textbf{Document Authentication system with QR-code}\\\\
\begin{itemize}
\item  \textsl{Description} : A prototype software to secure hard copy document from fraud and forgery by using 2D barcode tag containing some encrypted text from the orginal document so the other side can decrypt it and verify that no forgery occurs.

\item  \textsl{Technology/Libraries:} C\# , Public/Private key encryption, QR-Code, .Net Gemalto Smart card.
\end{itemize}

\end{itemize}
   %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Technical Skills: } 

\begin{tabular}{ l  l }

 %\rowcolor{gray} \color{white}{ \textbf{Programming Languages:}} & \\
\multicolumn{2}{l}{\textbf{Programming languages}} \\
& C ,C++, Java, PHP, Java Script, C\# and x86 Assembly. \\

\multicolumn{2}{l}{\textbf{Frameworks}} \\
& Qt, .Net, Android and CodeIgniter \\

 %\rowcolor{gray} \color{white}{ \textbf{DBMS:}} & \\
\multicolumn{2}{l}{\textbf{DBMS}} \\
& MySQL, SQLite, PostgreSQL ,MS SQL Server and Oracle .\\
 
%\multicolumn{1}{| >{\columncolor[rgb]{0.8,0.8,0.8}}l|}{Applied Knowledge:} & \\
\multicolumn{2}{ l}{\textbf{Applied Knowledge}} \\
& UML/OOP/Design Patterns \\
& Object oriented system analysis and design \\
& Relational database design \\
& Debugging and unit testing \\
& Coding style and documentation \\
& Linux RedHat Enterprise 5 administration,networking and security skills \\


 %\rowcolor{gray} \color{white}{ \textbf{Open Source Application/Tools/Libs:}} & \\
\multicolumn{2}{l}{\textbf{Open Source Application/Tools/Libraries}} \\
& GNU's tools and libraries\\
& Asterisk : VOIP,PBX \\
& Content management system: Joomla,wordpress \\
& Control Version Managements: git,svn,cvs\\
& Bug and Issue tracking system: Trac,mantisbt \\
& \LaTeX{} typesetting system\\
\end{tabular}


    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle  Awards} 
Nokia Qt Ambassador \hfill \textbf{July 2011}\\
2nd place for University of Khartoum - Faculty of Mathematical sciences "School Got Talent" programming competition.\hfill \textbf{May 2010}\vspace{-3mm}\\\vspace{-1mm}%

    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle  Training} 

International Turnkey Systems (ITS) in Sudan.\hfill \textbf{July 2010}\vspace{-3mm}\\\vspace{-1mm}%


  %__________________________________________________________________________________________________________________
    % Publications
     % \section{\mysidestyle Selected Articles on Internet }
   %  ``Design and implementation of operating system'',
    %  \textsl{University of Khartoum},2010.


  %\vspace{-2mm}
  %   ``Cross platform development with Qt'',
    %  \textsl{Qt arabic community},2008.

  %\vspace{-2mm}
  %   ``Data structure for absolute beginners'',
    %  \textsl{Visual C for arab web site},2007.

  %\vspace{-2mm}


    %__________________________________________________________________________________________________________________
    % Projects
    \section{\mysidestyle Academic\\ Projects}

\textbf{eqraOS}: An open source operating system written from scratch for academic purpose (graduate's project), it support alot of modern OS’s features like 32-bit PMode,Interrupt-based,Hybrid Kernel,HAL layer,Basic C++ runtime support,Virtual Memory with paging,support up-to 4 GiB physical memory,FAT12 file system,Keyboard driver and Boot from USB/CD (C/C++,Assembly).
\vspace{-2mm}


\textbf{Al-Moazen}: Cross platform GUI application for calculating Muslim prayers times by a powerful mathematical equations. it has a handful of features like Azan, Azkar and ability to run on Windows,Linux,Embedded devices and Mac OS X (C++/Qt).
\vspace{-2mm}


\textbf{SMS server}: Linux Application for sending and receiving SMS by connect a GSM modem to the computer (C++).
\vspace{-2mm}

\textbf{Function plotter}: Cross platform mathematical functions plotter, it can draw all mathematical functinos. (C++/Qt).
\vspace{-2mm}

\textbf{Al-Nozom managment system}: System for managing Al-Nozom company in Saudi Arabia, it was targeted to work in Windows,Linux and Nokia Symbian Mobiles (C++/Qt).
\vspace{-2mm}

\textbf{Al-Mymana medical accouting system}: System for managing accounts for Al-Mymana Medical in Sudan (C++/Qt).
\vspace{-2mm}

\textbf{Mobile Game}: TicTacToe for Nokia Symbian mobiles, it has two game modes: standard and extension mode and it support online playing with Internet or Bluetooth. Also the player can choose to play to other player or to the AI mobile.(C++/Qt).\\
\vspace{-2mm}




    %__________________________________________________________________________________________________________________
    %  Community\\Experience
\section{\mysidestyle  Community\\Experience} 
Cross platform Administration in \url{http://arabteam2000.com} website.\hfill \textbf{2009 - present}\vspace{-2mm}

Moderating Computer science community in Sudan \url{http://sudancs.com}.\hfill \textbf{2008 - present}\vspace{-2mm}

Moderating Qt Arabic community \url{http://qt-ar.org} website.\hfill \textbf{2008 - present}\vspace{-3mm}\\\vspace{3mm}

    %__________________________________________________________________________________________________________________
    % Language
\section{\mysidestyle Language}
	\textbf{Arabic}:   native language.\\
	\textbf{English}: working knowledge (excellent in reading, good in speaking \& listening).\\

    %__________________________________________________________________________________________________________________
    % Personal Skills
\section{\mysidestyle Personal\\Skills}
	Interactive and able to learn new technologies and Languages.\\
	Perfect ability to meet deadlines and work under pressure.\\
	Ability to work individual and as part of a team.\\
	Ability to think "outside the box".

    %__________________________________________________________________________________________________________________
    % Referees
    \section{\mysidestyle Referees} 
    {\sl Available on request.}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

